Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-06-07 SIR_manuscript.tex
LaTeX cleanup
recover discussion PP

%% FIXME: uncomment when this pipeline is working
\input{codes/modeldefs.tex}

@@

>>>>

\input{codes/modeldefs.tex}

@@

In this paper, we have defined and analyzed a simple compartmental model that combines epidemiological dynamics (as defined by a simple SIR model) with the dynamics of testing and isolation. Our model is a caricature --- it models the most basic feedbacks between epidemic and testing processes, but does not attempt to incorporate the many known complications of COVID-19 epidemiology (e.g. exposed, presymptomatic, and asymptomatic compartments [REFS]; time-varying testing rates [REFS?]; behavioural dynamics [REF Weitz/Park/Dushoff]). Thus, it is most appropriate for assessing the \emph{qualitative} phenomena that arise from the interactions between epidemiology and testing, rather than for making quantitative predictions or guiding pandemic responses.

Many of the qualitative results we have derived are mathematical confirmations of simple, common-sense intuitions. In particular, we can decrease $\Rnum$ by increasing isolation efficacy or testing intensity; returning tests faster, if individuals do not isolate while they are waiting for results; or increasing testing focus to target individuals who are likely to be infectious (e.g. symptomatic people or close contacts of known infections).
